Approximate Code: A Cost-Effective Erasure Coding Framework for Tiered Video Storage in Cloud Systems

### 2019-04-19 ApproximateCode.tex
version 3.8

\title{Approximate Code: A Cost-Effective Erasure Coding Framework for Video Applications in Cloud Storage Systems}

@@

With the increasing demand on higher resolution and frame rate for video data, tremendous storage devices are highly desired in cloud storage systems, which makes data centers much bigger. On YouTube, nearly 140,000 hours of video are played every minute and 400 hours of video are uploaded [DESCRIBE AND CITE YOUTUBE]. Therefore, in this paper, we set out to answer the following question,
In a cloud storage system, how to efficiently store the tremendous video data in 3DFTs?

To reduce the storage cost in cloud storage systems, a feasible solution is approximate storage. [DESCRIBE AND CITE APPROXIMATE STORAGE] but the data reliability cannot be guaranteed. Another solution is using disk arrays like RAID-5 or RAID-6 [CITE RAID], but the capability of fault tolerance should be sacrificed. Therefore, existing solutions cannot provide low storage cost and high reliability simultaneously.

@@

The rest of the paper is organized as follows. In Section \ref{RelatedWork}, we introduce related work and our motivation. 
In Section \ref{ApCode}, the design of Approximate Code and its encoding and decoding process will be illustrated in detail. 
Section \ref{Implementation} introduce the implementation of our design, and section \ref{ap-recovery} analysis the performance of approximate video storage.
The evaluation is presented in Section \ref{evaluation} and the conclusion of our work is in Section \ref{Conclusion}.

\section{Related Work and Our Motivation}\label{RelatedWork}
In this section, we introduce the background of Video frame recovery, existing solutions to reduce storage cost and the motivation of this paper.
To facilitate the discussion, we summarize the symbols used in this paper in Table \ref{parameter}.

\begin{table}[]
\caption{The symbols used in this paper.}\label{parameter}
\centering
\begin{tabular}{|c|l|}
\hline
Symbols & Description \\ \hline
$k$ & the number of data nodes in an array \\ \hline
$r$ & the number of local parity nodes in an array \\ \hline
$n$ & the number of nodes in an array ($n=k+r$) \\ \hline
$h$ & the number of arrays \\ \hline
$s$ & the number of blocks in a node \\ \hline
LP & local parity nodes \\ \hline
GP & global parity nodes \\ \hline
ID & important data \\ \hline
UD & unimportant data \\ \hline
 &  \\ \hline
\end{tabular}
\end{table}

@@

In the past two decades, several
famous erasure codes are proposed for double Disk Failure Tolerant arrays (2DFTs or RAID-6), such as EVENODD
code [1], RDP code [8], Blaum-Roth code[3], X-code [44], Liberation code [28], Liber8tion code [27], Cyclic [7] code, B-Code [45], Code-M [40], H-code [43], P-code [20] and HVcode [36], etc.

In Triple Disks Failure Tolerant Arrays (3DFTs), typical MDS codes include Reed-Solomon codes [33], Cauchy-RS codes [4], STAR code [19], Triple-Star code [41], Triple-Parity code [9], HDD1 code [39], RSL-code [10], RL-code [11], and so on. Typical non-MDS codes contain WEAVER codes [14], HoVer
codes [13], T-code [38], HDD2 code [39], Pyramid codes [18], Local Reconstruction Codes [16], Locally Repairable Codes [34], etc.

@@

\subsection{Video Frame Recovery}

In the circumstance of video approximate storage, it's common to lose some frames and leave the video incomplete. However, the lost frames may still be recoverable with the benefit of nowadays powerful deep learning techniques. One of them is named video frame interpolation.

Video frame interpolation is one of the basic video processing techniques, an attempt to synthetically produce one or more intermediate video frames from existing ones, the simple case being the interpolation of one frame given two consecutive video frames. This is a technique that can model natural motion within a video, and generate frames according to this modelling. Artificially increasing the frame-rate of videos enables the possibility of frame recovery.

\subsection{Approximate Storage}
Storage techniques nowadays generally regard all information of the same importance, which causes significant costs in energy, disk drives and computing resources. But not all data need high-reliability storage for its backup. That is when the concept of approximate storage is introduced. Approximate Storage is another way outside of traditional methods of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.

@@

However, it is too naive to store data in approximate storage units indiscriminately. Related research \cite{guo2016high} shows that this can lead to unacceptable data pollution. To ensure data quality in this case, higher error correction costs are required resulting in an increase in overall storage costs.
Therefore, it is very important to distinguish the importance of video data. This can usually be done by an experienced expert or automatically by a program.

\begin{table}[ht]
\centering 
\caption{Comparison of fault tolerance and storage overhead between approximate storage, EC and Approximate Code}\label{tab-AS-EC-AP}
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Schemes}  & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Realibilities & Performance \\ \hline\hline
\multirow{2}{*}{EC} & RS & high & high & medium \\ \cline{2-5} 
\multicolumn{1}{|c|}{} & RAID 6 & medium & medium & high \\ \hline
\multicolumn{2}{|c|}{Ap-Storage}& low & low & high \\ \hline
\multirow{2}{*}{Ap-Code}& Imp & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
 & Unimp &  & medium & high \\ \hline
\end{tabular}
\end{table}

@@

First, existing erasure codes generally reach or exceed 3DFTs, and use more than 3 parity disks. However, the simultaneous damage of 3 disks is very rare, and the storage overhead paid for this is too large. Second, the existing erasure codes provide the same fault tolerance for all data without distinction, which results in the same reliability of important data that is sensitive to errors and data that is robust. Last but not least, the current approximate storage methods are unreliable since they are not designed to tolerate disk level failure.

To solve these problems, we propose a new erasure code called Approximation Code. It provides different fault tolerance for important and non-critical data to reduce storage overhead and protect critical data better.

@@

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{photo/Framework.pdf}
\caption{The framework of Approximate Code}
\label{fig-framework}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{photo/AP-kmha-v7.pdf}
\caption{A sample of Approximate Codes $(4,1,4)$ in \emph{Structure 1}, and Approximate Code $(3,1,3)$ in \emph{Structure 2}.
Data nodes are marked as $N_i$, important data are marked as water green, local parity nodes are marked as orange and global parity nodes are marked as red.
}
\label{fig-ap-414}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.3\textwidth]{photo/AP-516.pdf}
\caption{The XOR-based Approximate Code ($5,1,6$, \emph{Structure 1}), constructed based on RAID5 and TIP-code.}
\label{fig-ap-TIP}
\end{figure}

\begin{figure}[h]

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{photo/AP-523.pdf}
\caption{The XOR-based Approximate Code ($5,2,4$), constructed based on EVENODD and STAR code. $LP$ represent the local parity and $GP$ represent the global parity.}
\label{fig-ap-STAR}
\end{figure}

\begin{figure}[ht]

@@

\begin{table}[ht]
\centering 
\caption{Comparison of storage overhead and fault tolerance between Ap-Code (short for Approximate Code), RS and several XOR-based codes.}\label{tab-AS-RS-AP}
\begin{tabular}{|c|c|c|c|}
\hline
EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault \\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Single Node\\Update Cost\end{tabular} \\ \hline
RS($k,r$) & $(k+r)/k$ & $r$ & r \\ \hline
EVENODD($k,2$) & $(k+2)/k$ & 2 & 2 \\ \hline
TIP-code/STAR($k,3$) & $(k+r)/k$ & 3 & 3 \\ \hline
\begin{tabular}[c]{@{}c@{}}Ap-Code\\ ($k,r,h$)\end{tabular} & $\frac {(k+r)h+3-r}{k \times h}$ & r to 3 & $r+\frac{3-r}{h}$ \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\begin{tabular}{|l|l|}
\hline
Description & DELL R730 Server \\ \hline
CPU & Intel Xeon 3.0GHz \\ \hline
NIC 1Gbps & 1Gbps \\ \hline
Memory & 32GB \\ \hline
Disk & 8TB HDD \\ \hline
OS & Linux 3.19 \\ \hline
Platform & Hadoop HDFS 3.0.3 \\ \hline
\end{tabular}
\caption{Details of Our Evaluation Platform}\label{tab-platform}
\end{table}

@@

\begin{figure*}[ht]
\subfigure[AP and RS]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example1Modi2.jpg}
}
\subfigure[AP and STAR]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example2Modi1.jpg}
}
\subfigure[AP and TIP]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example3.jpg}
}
\subfigure[AP and LRC]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example4.jpg}
}
\caption{Encoding Time Comparison between AP method and other method}\label{fig-encoding}
\end{figure*}

\begin{figure*}[ht]
\subfigure[AP and RS]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example5Modi1.jpg}
}
\subfigure[AP and STAR]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example6.jpg}
}
\subfigure[AP and TIP]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example7.jpg}
}
\subfigure[AP and LRC]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example8.jpg}
}
\caption{Decoding Time Comparison in One Disk between AP method and other method}\label{fig-decoding-1}
\end{figure*}

\begin{figure*}[ht]
\subfigure[AP and RS]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example9.jpg}
}
\subfigure[AP and STAR]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example10.jpg}
}
\subfigure[AP and TIP]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example11Modi1.jpg}
}
\subfigure[AP and LRC]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example12.jpg}
}
\caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-2}
\end{figure*}

@@

\begin{figure*}[ht]
\subfigure[Encoding Time]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/BarEnT.jpg}
}
\subfigure[Decoding Time in One Node Failure]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/BarDeT1Modi1.jpg}
}
\subfigure[Decoding Time in Two Node Failure]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/BarDeT2.jpg}
}
\caption{Comparison of several matrics between different methods when number of data nodes are 5}\label{fig-BAR}
\end{figure*}

>>>>

\title{Approximate Code: A Cost-Effective Erasure Coding Framework for Tiered Video Storage in Cloud Systems}

@@

With the increasing demand on higher resolution and frame rate for video data, massive storage devices are highly desired in cloud storage systems, which makes data centers much bigger.
Therefore, in this paper, we set out to answer the following question,
\textbf{In a cloud storage system, how to efficiently store the tremendous video data in 3DFTs?}

To reduce the storage cost in cloud storage systems, a feasible solution is approximate storage. Approximate storage exposes unimportant data to errors, saving the overhead of redundant backups [CITE APPROXIMATE STORAGE], thus the data reliability cannot be guaranteed. 
Another solution is using disk arrays like RAID-5 or RAID-6 [CITE RAID], but the capability of fault tolerance would be sacrificed.
Data compression\footnote{We do not discuss video compression technology much in this paper because it is an application layer algorithm and can be used with our scheme.} is also a common strategy for reducing storage overhead \cite{ziv1977universal} \cite{ziv1978compression} \cite{deutsch1996deflate}. However, the compression and decompression process results in very large computational overhead, high recovery speed and high response time, which is not suitable for video applications.
Therefore, existing solutions cannot provide low storage cost and high reliability simultaneously.

@@

The rest of the paper is organized as follows. In Section \ref{RelatedWork}, we introduce related work and our motivation. 
In Section \ref{ApCode}, the design of Approximate Code and its encoding and decoding process will be illustrated in detail. 
%Section \ref{Implementation} introduce the implementation of our design, and section \ref{ap-recovery} analysis the performance of approximate video storage.
The evaluation is presented in Section \ref{evaluation} and the conclusion of our work is in Section \ref{Conclusion}.

\section{Related Work and Our Motivation}\label{RelatedWork}
In this section, we introduce the background of video storage, existing solutions to reduce storage cost and the motivation of this paper.
To facilitate the discussion, we summarize the symbols used in this paper in Table \ref{parameter}.

\begin{table}[]
\caption{The symbols used in this paper.}\label{parameter}
\centering
\begin{tabular}{|c|l|}
\hline
Symbols & Description \\ \hline
$k$ & the number of data nodes in an array \\ \hline
$r$ & the number of local parity nodes in an array \\ \hline
$n$ & the number of nodes in an array ($n=k+r$) \\ \hline
$h$ & the number of arrays \\ \hline
$g$ & the number of global parity nodes \\ \hline
LP & local parity nodes \\ \hline
GP & global parity nodes \\ \hline
ID & important data \\ \hline
UD & unimportant data \\ \hline
\end{tabular}
\end{table}

\subsection{Basis of Video Storage}\label{video storage}
For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded by lossy algorithms before storage.

\subsubsection{Video coding}
H.264 is one of the advanced algorithms for this type of work. This coding technique is widely used on platforms such as YouTube because it has higher compression ratio and lower complexity than its predecessor. For the HD video mentioned earlier, H.264 can reduce its size by about 10 times, only 443.27MB.

H.264 classifies all frames into three different categories:
\begin{enumerate}
    \item I frame: A frame that does not depend on other frame data, which means it can be decoded independently of other frames.
    \item P frame: A frame holds the changes compared to the previous frame, thus saving much space by leaving out redundant information.
    \item B frame: A frame saves more space by utilizing the data of both the preceding and following frame.
\end{enumerate}
A GOP consists of multiple consecutive I, P, and B frames that are independent of frames in other GOPs to prevent bit error spread.
%In other words, a P or B frame can only reference the ones inside the GOP which it belongs to, as shown in Figure \ref{H264-IPB}. 
Therefore, within each GOP, the I frame has the highest importance because other frames rely on it for recovery; the importance of the P frame is second, and the B frame has the least importance. Based on this feature, a special program can be designed to distinguish the importance of video frames.

\iffalse
\begin{figure}[]
\centering
\includegraphics[width=0.45\textwidth]{photo/H264_IPB.pdf}
\caption{A sample of GOPs in H.264}
\label{H264-IPB}
\end{figure}
\fi

\subsubsection{Video Frame Recovery}
In the circumstance of video approximate storage, it's common to lose some frames and leave the video incomplete. However, the lost frames may still be recoverable with the benefit of nowadays powerful deep learning techniques. One of them is named video frame interpolation [CITE][CITE].

Video frame interpolation is one of the basic video processing techniques, an attempt to synthetically produce one or more intermediate video frames from existing ones.This is a technique that can model natural motion within a video, and generate frames according to this modelling.

@@

In the past two decades, several
famous erasure codes are proposed for double Disk Failure Tolerant arrays (2DFTs or RAID-6), such as EVENODD code [CITE], RDP code [CITE], Blaum-Roth code[CITE], X-code [CITE], Liberation code [CITE], Liber8tion code [CITE], Cyclic [CITE] code, B-Code [CITE], Code-M [CITE], H-code [CITE], P-code [CITE] and HVcode [CITE], etc.

In Triple Disks Failure Tolerant Arrays (3DFTs), typical MDS codes include Reed-Solomon codes [CITE], Cauchy-RS codes [CITE], STAR code [CITE], Triple-Star code [CITE], Triple-Parity code [CITE], HDD1 code [CITE], RSL-code [CITE], RL-code [CITE], and so on. Typical non-MDS codes contain WEAVER codes [CITE], HoVer
codes [CITE], T-code [CITE], HDD2 code [CITE], Pyramid codes [CITE], Local Reconstruction Codes [CITE], Locally Repairable Codes [CITE], etc.

@@

\subsection{Approximate Storage}
%Storage techniques nowadays generally regard all information of the same importance, which causes significant costs in energy, disk drives and computing resources. But not all data need high-reliability storage for its backup. That is why the concept of approximate storage is introduced. 
Approximate Storage is another way outside of traditional methods of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.

@@

%However, it is too naive to store data in approximate storage units indiscriminately. Related research \cite{guo2016high} shows that this can lead to unacceptable data pollution. To ensure data quality in this case, higher error correction costs are required resulting in an increase in overall storage costs. Therefore, it is very important to distinguish the importance of video data.

\begin{table}[ht]
\centering 
\caption{Comparison of storage overhead, reliability and performance between EC, Approximate Storage and Approximate Code. (``Appr.'' is short for ``Approximate'')}\label{tab-AS-EC-AP}
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Schemes} & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Reliability & Performance \\ \hline
\multirow{2}{*}{EC} & RS & high & high & medium \\ \cline{2-5} 
 & RAID-6 & medium & medium & high \\ \hline
\multicolumn{2}{|c|}{Appr. Storage} & low & low & high \\ \hline
\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Appr.\\ Code\end{tabular}} & ID & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
 & UD &  & medium & high \\ \hline
\end{tabular}
\end{table}

@@

First, the overhead of existing 3DFTs erasure codes is too high.
Second, the 2DFTs erasure codes sacrifice part of reliability, and the reliability of approximate storage schemes are much lower since they cannot tolerate disk-level failures.
Finally, existing erasure codes provide the same fault tolerance for all data without distinction, resulting in the same reliability for error-sensitive data and robust data.

Based on these reasons, we propose a scheme for tiered video storage in a highly reliable environment, Approximate Code.
Approximate code is an erasure code framework that uses tiered storage\cite{krish2014hats} \cite{wang2014balancing} \cite{zhang2010automated} \cite{udipi2012lot} and approximate storage strategies to separate an existing erasure codes into codes with different fault tolerances and apply them to important and unimportant data.

@@

\begin{figure}[]
\centering
\includegraphics[width=\linewidth]{photo/Framework.pdf}
\caption{The framework of Approximate Code}
\label{fig-framework}
\end{figure}

@@

\begin{figure}[]
\centering
\includegraphics[width=\linewidth]{photo/AP-kmha-v7.pdf}
\caption{A sample of Approximate Codes $(4,1,4)$ in \emph{Structure 1}, and Approximate Code $(3,1,3)$ in \emph{Structure 2}.
Data nodes are marked as $N_i$, important data are marked as water green, local parity nodes are marked as orange and global parity nodes are marked as red.
}
\label{fig-ap-414}
\end{figure}

@@

\begin{figure}[]
\centering
\includegraphics[width=0.3\textwidth]{photo/AP-516.pdf}
\caption{The XOR-based Approximate Code ($5,1,6$, \emph{Structure 1}), constructed based on RAID5 and TIP-code.}
\label{fig-ap-TIP}
\end{figure}

\begin{figure}[]

@@

\begin{figure}[]
\centering
\includegraphics[width=0.45\textwidth]{photo/AP-523.pdf}
\caption{The XOR-based Approximate Code ($5,2,4$), constructed based on EVENODD and STAR code. $LP$ represent the local parity and $GP$ represent the global parity.}
\label{fig-ap-STAR}
\end{figure}

\begin{figure}[]

@@

\begin{table}[]
\centering 
\caption{Comparison of storage overhead and fault tolerance between Ap-Code (short for Approximate Code), RS and several XOR-based codes.}\label{tab-AS-RS-AP}
\begin{tabular}{|c|c|c|c|}
\hline
EC & \begin{tabular}[]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[]{@{}c@{}}Fault \\ Tolerance\end{tabular} & \begin{tabular}[]{@{}c@{}}Single Node\\Update Cost\end{tabular} \\ \hline
RS($k,r$) & $(k+r)/k$ & $r$ & r \\ \hline
EVENODD($k,2$) & $(k+2)/k$ & 2 & 2 \\ \hline
TIP-code/STAR($k,3$) & $(k+r)/k$ & 3 & 3 \\ \hline
\begin{tabular}[]{@{}c@{}}Ap-Code\\ ($k,r,h$)\end{tabular} & $\frac {(k+r)h+3-r}{k \times h}$ & r to 3 & $r+\frac{3-r}{h}$ \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[]
\begin{tabular}{|l|l|}
\hline
Description & DELL R730 Server \\ \hline
CPU & Intel Xeon 3.0GHz \\ \hline
NIC 1Gbps & 1Gbps \\ \hline
Memory & 32GB \\ \hline
Disk & 8TB HDD \\ \hline
OS & Linux 3.19 \\ \hline
Platform & Hadoop HDFS 3.0.3 \\ \hline
\end{tabular}
\caption{Details of Our Evaluation Platform}\label{tab-platform}
\end{table}

@@

\begin{figure*}[]
\subfigure[AP and RS]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example1Modi2.jpg}
}
\subfigure[AP and STAR]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example2Modi1.jpg}
}
\subfigure[AP and TIP]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example3.jpg}
}
\subfigure[AP and LRC]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example4.jpg}
}
\caption{Encoding Time Comparison between AP method and other method}\label{fig-encoding}
\end{figure*}

\begin{figure*}[]
\subfigure[AP and RS]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example5Modi1.jpg}
}
\subfigure[AP and STAR]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example6.jpg}
}
\subfigure[AP and TIP]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example7.jpg}
}
\subfigure[AP and LRC]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example8.jpg}
}
\caption{Decoding Time Comparison in One Disk between AP method and other method}\label{fig-decoding-1}
\end{figure*}

\begin{figure*}[]
\subfigure[AP and RS]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example9.jpg}
}
\subfigure[AP and STAR]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example10.jpg}
}
\subfigure[AP and TIP]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example11Modi1.jpg}
}
\subfigure[AP and LRC]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/Example12.jpg}
}
\caption{Decoding Time Comparison in Two Disk between AP method and other method}\label{fig-decoding-2}
\end{figure*}

@@

\begin{figure*}[]
\subfigure[Encoding Time]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/BarEnT.jpg}
}
\subfigure[Decoding Time in One Node Failure]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/BarDeT1Modi1.jpg}
}
\subfigure[Decoding Time in Two Node Failure]{
    \includegraphics[width = 0.23\linewidth]{photo/experiment/BarDeT2.jpg}
}
\caption{Comparison of several matrics between different methods when number of data nodes are 5}\label{fig-BAR}
\end{figure*}
